Debiased Calibration for Generalized Two-Phase Sampling

### 2024-04-11 final/reports/prelim_paper.tex
Working on TP DC simulation. About to switch from SRS to Poisson sampling because then I can actually use the debiased calibration. Hopefully, the GEcalib function will then work.

\title{Debiased calibration for generalized two-Phase sampling}
\author{Caleb Leedy}
\maketitle

@@

\textcolor{red}{Dr. Kim: Should I provide the proof for design unbiasedness of
$\hat Y_{\pi^*}$? } \textcolor{blue}{Not necessary. You may cite a book or a paper  for this claim. }

While unbiased, the $\pi^*$-estimator unfortunately does not account for the
additional information contained in the auxiliary Phase 1 variable $X$. The
two-phase regression estimator $\hat Y_{reg, tp}$ does incorporate \textcolor{blue}{$\hat{X}_1$ obtained from the phase one sample. That is, we can leverage the external information $\hat{X}_1$ to improve the $\pi^*$-estimator in the second-phase sample. } 
The two-phase 
regression estimator has the form,

@@

This means that $\hat Y_{reg, tp}$ is also a calibration estimator. The idea
that regression estimation is a form of calibration was extended by 
\cite{deville1992calibration} to consider loss functions other than just squared
loss. They generalized the loss function to minimize $\sum_i G(w_i, d_i)q_i$ for
weights $w_i$ and design-weights $d_i$ where $G()$ is non-negative, strictly
convex function with respect to $w$, defined on an interval containing $d_i$,
with $g(w_i, d_i) = \partial G / \partial w$ continuous.
\footnote{The \cite{deville1992calibration} paper considers regression estimators
for a single phase setup, which we apply to our two-phase example. } This
generalization includes empirical likelihood estimation, and maximum entropy
estimation amoung others. The variance estimation is based on a linearization
that shows that minimizing the generalized loss function subject to the
calibration constraints is asymptotically equivalent to a regression estimator.

While this generalization is useful to an analyst who may want different
properties of their estimator from maximum entropy estimation rather than the
minimal squared loss, unless $\pi_{2i|1}^{-1} \in C(X)$, the estimator is not
design consistent. \footnote{ \textcolor{red}{I do not understand this part.} } 
Furthermore, at a conceptual level, the regression estimator
has a nice feature that its two terms can be thought about as minimizing
variance and bias correction,

$$ \hat Y_{reg, tp} 
= \underbrace{\sum_{i \in A_1} \frac{x_i \hat \beta_2}{\pi_i^{(1)}}}_{Minimizing
the variance} + \underbrace{\sum_{i \in A_2}
\frac{1}{\pi_i^{(1)}\pi_{2i|1}^{(2)}} (y_i - x_i \hat \beta_2)}_{Bias
correction}.$$

@@

\begin{theorem}(Asymptotic Normality)

>>>>

\title{Debiased Calibration for Generalized Two-Phase Sampling}
\author{Caleb Leedy}
\maketitle

@@

While unbiased \cite{kim2024statistics}, the $\pi^*$-estimator unfortunately
does not account for the additional information contained in the auxiliary Phase
1 variable $X$. The two-phase regression estimator $\hat Y_{reg, tp}$ does incorporate 
\textcolor{blue}{$\hat{X}_1$ obtained from the phase one sample. That is, we can
leverage the external information $\hat{X}_1$ to improve the $\pi^*$-estimator
in the second-phase sample. } 
The two-phase regression estimator has the form,

@@

This means that $\hat Y_{reg, tp}$ is also a calibration estimator. The idea
that regression estimation is a form of calibration was extended by 
\cite{deville1992calibration} to consider loss functions other than just squared
loss. They generalized the loss function to minimize $\sum_i G(w_i, d_i)q_i$ for
weights $w_i$ and design-weights $d_i$ where $G(\cdot)$ is non-negative, strictly
convex function with respect to $w$, defined on an interval containing $d_i$,
with $g(w_i, d_i) = \partial G / \partial w$ continuous.
\footnote{The \cite{deville1992calibration} paper considers regression estimators
for a single phase setup, which we apply to our two-phase example. } This
generalization includes empirical likelihood estimation, and maximum entropy
estimation amoung others. The variance estimation is based on a linearization
that shows that minimizing the generalized loss function subject to the
calibration constraints is asymptotically equivalent to a regression estimator.

While this generalization is useful to an analyst who may want different
properties of their estimator from maximum entropy estimation rather than the
minimal squared loss, 
% TODO: I am not sure if this is correct -----
unless $\pi_{2i|1}^{-1} = x_i'a$ for some $a$, the
estimator is not design consistent. 
\footnote{ \textcolor{red}{I do not understand this part.} I changed the
notation so that it would not be the unused column space notation. This is from
Equation (11.17) of \cite{kim2024statistics}.} 
% --------------------------------------------

Furthermore, at a conceptual level, the regression estimator
has a nice feature that its two terms can be thought about as minimizing
variance and bias correction,

$$ \hat Y_{reg, tp} 
= \underbrace{\sum_{i \in A_1} \frac{x_i \hat \beta_2}{\pi_i^{(1)}}}_{
  \text{ Minimizing the variance}} + \underbrace{\sum_{i \in A_2}
\frac{1}{\pi_i^{(1)}\pi_{2i|1}^{(2)}} (y_i - x_i \hat \beta_2)}_{
\text{Bias correction}}.$$

@@

\begin{theorem}(Asymptotic Normality)
% FIXME: Add result.
\end{theorem}
